---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

NOTE: This is a toy package created for expository purposes. It is not meant to actually be useful. 

# aminoamino

<!-- badges: start -->
<!-- badges: end -->

The goal of aminoamino is to automate the conversion from DNA to RNA, and from RNA to Amino Acid. 

## Installation

You can install the development version of aminoamino from [GitHub](https://github.com/) with:
      
``` r
# install.packages("devtools")
devtools::install_github("lingminhao/aminoamino")
```

## Usage
First, load the package. 
```{r}
library(aminoamino)
```

A common process in genomics is DNA to RNA conversion. DNA consists of a combination of 4 different nucleotide bases A, C, T and G. For example, ACTTTAAGC is a DNA string. 

The conversion from DNA to RNA is basically replacing the T base to a U base. We provide this functionality in this package: 

```{r}
dna <- "ACTTTAAGC"
transcription(dna)
```
